---
title: "HW Data Visualization"
author: "Patsawut Tananchai"
output:
  pdf_document: default
  html_notebook: default
---

# **diamonds anlaytics**


load lib
```{r}
library(dplyr)
library(tidyverse)
library(ggplot2)
```


```{r}
glimpse(diamonds)
```
Data Description
```{r}
?diamonds
```

A data frame with 53940 rows and 10 variables:

price - price in US dollars (\$326–\$18,823)

carat - weight of the diamond (0.2–5.01)

cut - quality of the cut (Fair, Good, Very Good, Premium, Ideal)

color - diamond colour, from D (best) to J (worst)

clarity -a measurement of how clear the diamond is (I1 (worst), SI2, SI1, VS2, VS1, VVS2, VVS1, IF (best))

x -length in mm (0–10.74)

y - width in mm (0–58.9)

z - depth in mm (0–31.8)

depth - total depth percentage = z / mean(x, y) = 2 * z / (x + y) (43–79)

table - width of top of diamond relative to widest point (43–95)


## Visualization

Relationships Between carat, price , color
```{r}
set.seed(42)
sample_daimonds <- sample_n(diamonds,1000)
ggplot(sample_daimonds, aes(carat, price , color = carat )) + 
  geom_point() + 
  theme_minimal() + 
  facet_wrap(~ clarity)
```
This graph shows that clarity doesn’t relate with the price but carat relate with price


number of cut , color
```{r}
ggplot(sample_daimonds, aes(cut, color , color = color )) + 
  geom_count() + 
  theme_minimal() 
```


Relationships Between carat , dept
```{r}
ggplot(sample_daimonds, aes(carat, depth , color = price )) + 
  geom_point() + 
  theme_minimal() 
```
This graph shows that dept doesn’t relate with the price but carat relate with price

```{r}
ggplot(sample_daimonds, aes(carat, price , color = color )) + 
  geom_point() + 
  theme_minimal() 
```
This graph shows that color doesn’t relate with the price but carat relate with price

count number of diamonds group by color

```{r}
  sample_daimonds %>%
    ggplot(aes(color , fill = color)) +
    geom_bar()
```

